---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sgat

<!-- badges: start -->
<!-- badges: end -->

The goal of sgat package is to retrieve information from Google's searches' "Popular Times" and geolocation.

## Installation

You can install the released version of sgat package from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("sgat")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("matiaspoullain/sgat")
```
## Example

Always start by initializing the driver, once per session:

```{r example, message=FALSE, warning=FALSE}
library(sgat)
initialization_sgat()
```

This package was created to use it on restaurants, bars, etc... located in Ushuaia city, Tierra del Fuego, Argentina. You can retrieve a vector them with the next code:

```{r restaurants, message=FALSE, warning=FALSE}
restaurants <- ushuaia_restaurants()
head(restaurants)
```

You can retrieve the information from some of these restaurants. A csv file will be created in the "CSVs Concurrencias" directory by default. The file's name is the string you looked for.

```{r bar 1, message=FALSE, warning=FALSE}
bar_1 <- sgat(restaurants[1], carpeta.guardado = "CSVs Concurrencias")
head(bar_1)
```

Although, some other Google searches doesn't have the wanted information. In that case, NULL is returned:

```{r bar 2, message=FALSE, warning=FALSE}
bar_2 <- sgat(restaurants[2])
bar_2
```

The searches are not restricted to Ushuaia, but remember to be specific in your searches, specially if the location you are lookinn for is far away:

```{r bar 3, message=FALSE, warning=FALSE}
bar_3 <- sgat("coutume, 47 rue de babylone, 75007 paris, france")
head(bar_3)
```
